Further Empirical Analyses of Rawlsian Fairness for Machine Learning

### 2017-05-10 paper/paper.tex
sentence pointer to figures
final

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{\emph{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the ``best" player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step). The learning algorithm appears to converge to approximately $50\%$ accuracy, which is considerably higher than the baseline.} \label{fig:yahoo}}
\end{figure*}

@@

@@

In this work, we present an empirical extension of the work done by \newcite{DBLP:journals/corr/JosephKMNR16} in their paper \textit{Rawlsian Fairness for Machine Learning}. Specifically, we present implementations of their algorithms \textsc{TopInterval}, \textsc{IntervalChaining}, and \textsc{RidgeFair}; a case study in which we apply the aforementioned algorithms to a Yahoo! clicks dataset; and an extension of one of \newcite{DBLP:journals/corr/JosephKMNR16}'s empirical analyses on randomly generated data. We believe that both our results may be useful should these algorithms be used in future real-world settings.

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the ``best" player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step). The learning algorithm appears to converge to approximately $50\%$ accuracy, which is considerably higher than the baseline. \label{fig:yahoo}}
\end{figure*}

@@

We present our results in Figures \ref{fig:free_T}, \ref{fig:free_k}, and \ref{fig:free_d}.

@@

In this work, we present an empirical extension of the work done by \newcite{DBLP:journals/corr/JosephKMNR16} in their paper \textit{Rawlsian Fairness for Machine Learning}. Specifically, we present implementations of their algorithms \textsc{TopInterval}, \textsc{IntervalChaining}, and \textsc{RidgeFair}; a case study in which we apply the aforementioned algorithms to a Yahoo! clicks dataset; and an extension of one of \newcite{DBLP:journals/corr/JosephKMNR16}'s empirical analyses on randomly generated data. We believe that our results may be useful should these algorithms be used in future real-world settings.
